\section{Command execution time analysis}\label{sec:cmd-dist}
In order to determine the performance of individual commands we created a fork of the worker that logged elapsed wall clock times for \textit{valid} commands.
A valid command is properly formatted (e.g.\ no negative dollar amounts) and meets all account state pre-conditions.
This assures a common execution path for results and prevents a multi-modal distribution caused by commands resolving early and avoiding lengthy inter-service communication delays.
Results are summarized in Table~\ref{tbl:cmd-dist}.

\begin{table}[htpb]
  \centering
  \caption[Command execution time percentiles]{Command execution times gathered from 3 runs of the 1000 user workload}
  \label{tbl:cmd-dist}
  \input{dist-table}
\end{table}

Command execution times show two general patterns.
Commands that do not use stock prices as pre-conditions (e.g.\ \textsc{Add}, \textsc{Commit Buy}, \textsc{Set Sell Amount}) resolve at a median time of $\approx \SI{25}{\micro\second}$.
Commands that do use stock prices resolve at a median time of $\approx \SI{220}{\micro\second}$.
The order of magnitude slow down is the result of storing stock values externally (but locally) in Redis.
The retrieval delay is costly but is countered by offloading quote TTL enforcement.

There are several interesting anomalies in Table~\ref{tbl:cmd-dist}.
The first is the paucity of data from \textsc{Sell} commands.
This is because the set of pre-conditions is the largest for any command: the user must have already purchased stock \textit{and} chosen a sell amount that resolve for pseudo-random stock prices. 

Next, the 99.99\% values for the non-stock, high-frequency commands increase by an order of magnitude compared to the 99.9\% values.
Since execution of these commands doesn't involve any external services the delay is likely the result an ill-timed application garbage collection cycle.
Since this delay doesn't manifest in the tails of the low-frequency events (e.g.\ \textsc{Cancel Sell}) the likelihood of being slowed by a garbage collection event is $\approx \frac{1}{30000}$.

\textsc{Dumplog} data is largely uninformative, given the extremely small sample size.
The execution time results from a path that necessarily interfaces with external services and is subject to communication delay.

\textsc{Buy} and \textsc{Quote} do exhibit bi-modal behaviors despite the experiment setup.
This is a result of quote cache hits and misses having execution times that differ by several orders of magnitude.
Histograms for all of the commands are presented in Appendix\improvement{Manually insert the appendix number}.
