---
title: "Quoteserver response time analysis"
author: "Tyler Stephen"
date: '2017-03-12'
output: pdf_document
---

We sent a large number of request to `quoteserve.seng.uvic.ca:4443` and recorded the delay of the response.

```{r read data, echo=FALSE}
times <- read.csv("times.csv", header = F, col.names = c("time"))
times <- times * 1000 # convert sec -> msec
```

```{r delay hist, echo=FALSE}
h = hist(times$time, breaks = c(0, 1000, 2000, 3000, 4000, 5000), plot = F)
h$density = h$counts / sum(h$counts) # change densities to percents
plot(h,
     freq = F,
     col = "lightgreen",
     ylim = range(0:1),
     ylab = "Relative frequency",
     xlab = "Response time (ms)",
     main = bquote("quoteserver response times," ~ n == 1200)
     )
```

The expected response time in milliseconds is
```{r expected resp delay, echo=FALSE}
ev = weighted.mean(h$counts, (h$counts / sum(h$counts)))
print(ev)
```

The above historgram uses one second buckets and hides the fact that the delays are clustered after whole second values. Removing the constant delay portion from each bucket yeilds the distribution of variable network and processing delays.

```{r resp var delay, echo=FALSE}
# Collect the offsets from each bucket starting point
allDelays = numeric()
for (i in 1:length(h$breaks) - 1) {
  delays = Filter(function(x) x >= h$breaks[i] && x < h$breaks[i+1], times$time)
  delays = delays - h$breaks[i]
  allDelays = append(allDelays, delays)
}

summary(allDelays)
```

The tail values are
```{r delay tail}
tail(sort(allDelays), 10)
```

Choosing an initial response timeout of 20 milliseconds and 5 millisecond exponential backoff requires 6 iterations to exceed the expected delay. This event has a likelihood of 0.1614%. Exceeding 1 second total delay has a likelihood of 0.0299%
```{r likelihoods, include = FALSE}
# Compute the values for the above analysis but don't include in the pdf
base = 20
backoff = 5
total = 0
i = 1
while (total <= ev) {
  backoff = backoff*2
  total = total + base + backoff
  i = i + 1
}
print(i - 1) # total iterations
print(total) # time for total iter
print((1 - h$density[1])**(i-1)) # likehood of exceeding EV
print((1 - h$density[1] )**(i-1) * (1 - h$density[1] - h$density[2])) # likehood of exceeding 1sec
```
