---
title: "Quoteserver response time verification"
author: "Tyler Stephen"
date: '2017-03-26'
output: pdf_document
---
```{r read data, echo=FALSE}
quotes20 <- read.csv("quotes-20ms.csv", header = T, col.names = c("time", "attempts"))
quotes20$time <- quotes20$time / 1e6 # convert ns -> ms
```
What's the response time distribution for single attempt quotes? (times in ms)
```{r single attempt times, echo=FALSE}
singleAttempts <- subset(quotes20, attempts==1)
quantile(singleAttempts$time, c(.95, .99, .995))
```
The initial test of the quoteserver inidicated that the tail of the response times would be bounded by 20ms. This data -- measured from the quote requesting service instead of a bash script -- indicates that almost all responses will resolve before 10ms.

```{r quick attempts, echo=FALSE}
quickAttempts <- subset(singleAttempts, time < 10)
h = hist(quickAttempts$time, plot=F)
plot(h,
     freq = F,
     col  = "lightgreen",
     ylim = range(0,1),
     ylab = "Relative frequency",
     xlim = range(0, 10),
     xlab = "Response time (ms)",
     main = "" # n = 2727
     )
```

We changed the request timeout to 10ms and re-ran the test.

```{r hist, echo=FALSE}
htime = hist(quotes20$time, plot=F)
htime$density = htime$counts / sum(htime$counts) # change density to percents
plot(htime,
     freq = F,
     col  = "lightgreen",
     ylim = range(0,1),
     ylab = "Relative frequency",
     xlab = "Response time (ms)",
     main = bquote("Total time waiting for quote," ~ n == 3964)
     )

hattempts = hist(quotes20$attempts, breaks = c(seq(1, 8)), plot=F)
plot(hattempts,
     freq = F,
     col  = "lightgreen",
     ylim = range(0,1),
     ylab = "Relative freqneucy",
     xlab = "Total attempts",
     main = bquote("Times retried before receiving quote," ~ n == 3964)
     )
```
